Ethnicity sensitive author disambiguation using semi-supervised learning

### 2016-01-12 paper/author_disambiguaton.tex
Further changes to the abstract

Author name disambiguation in bibliographic databases is the problem of
grouping together scientific publications written by the same person, accounting
for potential homonyms and/or synonyms.
Among solutions to this problem, digital libraries are increasingly offering tools
for authors to manually curate their publications and claim those that are theirs.
Indirectly, these tools allow for the inexpensive collection of large annotated training
data, which can be further leveraged to build a complementary automated
disambiguation system capable of inferring patterns for identifying
publications written by the same person.
Building on more than 1 million publicly released crowdsourced annotations,
we propose an automated author disambiguation solution exploiting this data (i) to learn
an accurate classifier for identifying coreferring authors and (ii) to guide the clustering
of scientific publications by distinct authors in a semi-supervised way.
To the best of our knowledge, our analysis is the first to be carried out on data of
this size and coverage.
With respect to the state of the art, we validate the general pipeline used in most existing
solutions, and improve by: (i) proposing phonetic-based blocking strategies, thereby
increasing recall; and (ii) adding strong ethnicity-sensitive features for learning a linkage
function, thereby tailoring disambiguation to non-Western author names whenever necessary.
\end{abstract}

>>>>

Author name disambiguation in bibliographic databases is the problem of grouping
together scientific publications written by the same person, accounting for
potential homonyms and/or synonyms. Among solutions to this problem, digital
libraries are increasingly offering tools for authors to manually curate their
publications and claim those that are theirs. Indirectly, these tools allow for
the inexpensive collection of large annotated training data, which can be
further leveraged to build a complementary automated disambiguation system
capable of inferring patterns for identifying publications written by the same
person. Building on more than 1 million crowdsourced
annotations that we publicly release, we propose an automated author disambiguation solution exploiting
this data (i) to learn an accurate classifier for identifying coreferring
authors and (ii) to guide the clustering of scientific publications by distinct
authors in a semi-supervised way. To the best of our knowledge, our analysis is
the first to be carried out on data of this size and coverage. With respect to
the state of the art, we validate the general pipeline used in most existing
solutions, and improve by: (i) proposing phonetic-based blocking strategies,
thereby increasing recall; (ii) adding strong ethnicity-sensitive features for
learning a linkage function, thereby tailoring disambiguation to non-Western
author names whenever necessary; and (iii) showing the importance of balancing
negative and positive examples when learning the linkage function.

\end{abstract}
